Python as a machine learning language: experiences from the scikit-learn project

### 2013-04-26 api.tex
typo

At each point is this grid, $k$-fold cross validation is run
to estimate the performance of the estimator according to some measure
(e.g.\ accuracy, $F_\beta$-score or a host of clustering quality metrics)
and the best performing set of hyperparameters is stored
on the \texttt{GridSearchCV} object; again, as a public attribute.

>>>>

At each point in this grid, $k$-fold cross validation is run
to estimate the performance of the estimator according to some measure
(e.g.\ accuracy, $F_\beta$-score or a host of clustering quality metrics)
and the best performing set of hyperparameters is stored
on the \texttt{GridSearchCV} object; again, as a public attribute.
